Investigating magnetic dynamo evolution with TESS field dwarfs

### 2017-10-05 ms.tex
removing exoplanet stuffs

% \author{R. Angus\altaffilmark{\columbia}
%         J. R. Davenport\altaffilmark{\ww}
%         D. Foreman-Mackey\altaffilmark{\cca},
%         S. Oh\altaffilmark{\princeton},
%         D. Busazi\altaffilmark{\florida},
%         A. Mann\altaffilmark{\columbia}
%         D. Kipping\altaffilmark{\columbia}
% }

% \altaffiltext{\columbia}{Department of Astronomy, Columbia University, New
% York, NY}
% \altaffiltext{\simons}{Simons Fellow, RuthAngus@gmail.com}
% \altaffiltext{\ww}{Western Washington University, Bellingham, WA}
% \altaffiltext{\nsf}{NSF Fellow}
% \altaffiltext{\florida}{Florida Gulf Coast University, Fort Myers, FL}
% \altaffiltext{\cca}{Center for Computational Astronomy, Flatiron Institute,
% New York, NY}
% \altaffiltext{\hubble}{Hubble Fellow}
% \altaffiltext{\princeton}{Princeton University, Princeton, NJ}

@@

Some outstanding mysteries regarding the nature of magnetic braking have been
revealed, but thus-far unanswered by, \kepler.
Firstly, a mysterious gap in the rotation period distribution of \Kepler\
dwarfs requires either a sharp transition in magnetic dynamo geometry or a gap
in the local star formation history as an explanation \citep{mcquillan2014,
davenport2017}.
Secondly, a transitioning magnetic dynamo appears to be responsible for
inefficient magnetic braking at old ages in Solar-mass stars.
{\bf We propose to help answer these questions by providing a catalog of \TESS\
rotation periods for FFI and CTL stars.}
We also intend to use gyrochronology in the cases where it {\it is} applicable
to learn about the evolution of exoplanets across the galaxy.

@@

Finally, we hope to use the improved gyrochronology relations, calibrated
using \TESS\ data to infer the dependence of planet frequency on age and
position in the galaxy.
\kepler\ revealed tantalizing hints that exoplanets on short orbital periods
have larger radii and are more infrequent around young stars \citep{mann2017a,
mann2017b, rizzuto2017}.
Do these trends continue into older ages and do they exist in the field?
We will answer these questions by measuring rotation periods for all \TESS\
field stars.

@@

The full set of available \TESS\ FFI and two-minute cadence light curves will
be exceedingly large and we intend to prioritize certain groups of stars for
period analysis, calculating a simple (and computationally fast) Lomb-Scargle
periodogram for the low priority objects and running a full probabilistic
period analysis on the high priority targets.
High priority targets include: comoving pairs, stars in the CVZs (especially
those with spectra), stars in TGAS, stars at large distances, any potential
asteroseismic dwarfs and exoplanet hosts.
% Of these, the stars that also lie in the CVZs as well as the identified \Gaia\
% comoving pairs will be our highest priority.
% Our next priority will be stars in the CVZs, with spectra, that do not appear
% in TGAS, followed by those without spectra.
% M dwarfs rotation periods in the CVZz will allow us to study the rotation
% period bimodality at lower masses, since the bimodality appears at longer
% rotation periods for lower mass stars.
% We will then focus on measuring rotation periods for a sample of stars that is
% representative of the full set of FFI and CTL targets in order to enable
% exoplanet population studies.
An large amount of computational resources are available to us, with access to
the Columbia supercomputer as well as facilities at the Flatiron Institute.
% We expect that each target will require around one minute of computation time
% and have access to around 10,000 computing hours.
% We therefore expect to analyze around 60,000 light curves.

>>>>

@@

Some outstanding mysteries regarding the nature of magnetic braking have been
revealed, but thus-far unanswered by, \kepler.
Firstly, a mysterious gap in the rotation period distribution of \Kepler\
dwarfs requires either a sharp transition in magnetic dynamo geometry or a gap
in the local star formation history as an explanation \citep{mcquillan2014,
davenport2017}.
Secondly, a transitioning magnetic dynamo appears to be responsible for
inefficient magnetic braking at old ages in Solar-mass stars.
{\bf We propose to help answer these questions by providing a catalog of \TESS\
rotation periods for FFI and CTL stars.}
% We also intend to use gyrochronology in the cases where it {\it is} applicable
% to learn about the evolution of exoplanets across the galaxy.

@@

% Finally, we hope to use the improved gyrochronology relations, calibrated
% using \TESS\ data to infer the dependence of planet frequency on age and
% position in the galaxy.
% \kepler\ revealed tantalizing hints that exoplanets on short orbital periods
% have larger radii and are more infrequent around young stars \citep{mann2017a,
% mann2017b, rizzuto2017}.
% Do these trends continue into older ages and do they exist in the field?
% We will answer these questions by measuring rotation periods for all \TESS\
% field stars.

@@

The full set of available \TESS\ FFI and two-minute cadence light curves will
be exceedingly large and we intend to prioritize certain groups of stars for
period analysis, calculating a simple (and computationally fast) Lomb-Scargle
periodogram for the low priority objects and running a full probabilistic
period analysis on the high priority targets.
High priority targets include: comoving pairs, stars in the CVZs (especially
those with spectra), stars in TGAS, stars at large distances, any potential
asteroseismic dwarfs and exoplanet hosts.
% Of these, the stars that also lie in the CVZs as well as the identified \Gaia\
% comoving pairs will be our highest priority.
% Our next priority will be stars in the CVZs, with spectra, that do not appear
% in TGAS, followed by those without spectra.
% M dwarfs rotation periods in the CVZz will allow us to study the rotation
% period bimodality at lower masses, since the bimodality appears at longer
% rotation periods for lower mass stars.
% We will then focus on measuring rotation periods for a sample of stars that is
% representative of the full set of FFI and CTL targets in order to enable
% exoplanet population studies.
% An large amount of computational resources are available to us, with access to
% the Columbia supercomputer as well as facilities at the Flatiron Institute.
% We expect that each target will require around one minute of computation time
% and have access to around 10,000 computing hours.
% We therefore expect to analyze around 60,000 light curves.
